`conmat`: generate synthetic contact matrices for a given age-stratified population

### 2025-08-06 paper/paper.qmd
add acknowledgements

>>>>

# Acknowledgements

The authors would like to thank Gerry Ryan for his contributions to conmat, as well as the authors of "Projecting social contact matrices in 152 countries using contact surveys and demographic data", Kiesha Prem, Alex Cook, and Mark Jit, for making their original data public. We would also like to thank reviewers Hugo Gruson and Anthony Baptista for their contributions.
